Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-06-27 manuscript/main.tex
intro paragraph simplified. no more eigenproblem

\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an  intermediate strategy for implementing the first step of the PLS algorithm. Specifically, the following proposition states a tractable generalized eigenvalue problem (i.e. maximization of a generalized Rayleigh quotient) that can be solved to directly obtain a hybrid PLS component $\widehat{\boldsymbol{\xi}}=(\widehat{\psi}, \widehat{\boldsymbol{\theta}})$, which has the same structure as the hybrid predictor $\mathbf{W}=(X,\mathbf{Z})$ of model \eqref{eq: Hybrid functional model}.

>>>>

	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm. This approach directly obtains a hybrid PLS component, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
